Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-27 paper/current/main.tex
Changes throughout—finish moving things around

A unique characteristic of semantic mobility embeddings is the ability to capture structure at multiple scales of granularity.
For example, just as the global embedding captures geographic structure between nations, so too does a projection or organizations in the United States reflect organizational structure based on states and oriented along an East-West axis (Fig.~\ref{fig:projection}d). 
My re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban Centers (Boston vs. Worcester), but also based on organization type (hospitals tend to be adjacent) and different university systems. Even though UMass Boston is located in Boston, it clusters near other universities in the UMass System, reflecting a relative lack of mobility between the two systems, even within the same state. 
Similar dynamics can be observed in many states (New York, California, etc.), such that prestigious university systems are separate from more regional ones (See SI~?).

@@

Based on descriptive findings, we more rigorously assess the extent to which embeddings capture the structure of international mobility. 
We calculate the representative vector of each country with averaging organization vectors within the given country, calculate pairwise cosine similarity, and perform hierarchical clustering (see Fig. \ref{fig:clustering}a).
Countries that have more than 25 organizations are collected for the clustering analysis, though we exclude the United States due to its high similarity with all other countries.

Six country clusters were identified, reflecting a mixture of the regional, linguistic, historical clusters. 
From top-to-bottom, we identify a primarily East-Asian cluster (orange), a Scandinavian cluster (dark purple), a cluster of British Commonwealth countries (light purple), a central and eastern European cluster (sky blue), a diverse cluster of European and South American clusters (dark green), and finally another diverse cluster consisting of countries bordering the Mediterranean or the Black Sea.
When not defined by geography, clusters appear to be defined by linguistic and historical ties, as is the case for the commonwealth countries. 
By looking closely at the deprogram and meta-data, there is a tendency that countries are merged as a group if they share the language in the early stage of the deprogram and geographical aspect plays a more major role in the later stage of the dendrogram.

We investigate the extent to which geography and language dictate the formation of clusters using \textit{CluSim}~\autocite{gates2019element}.
\textit{CluSim} is a method that calculates the similarity between the cluster results and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting likes ``zooming lens''.  
If $r$ is high, the similarity is based on the lower levels of the dendrogram, and when $r$ is low, similarity is based on higher levels dendrogram. 
In fig. \ref{fig:clustering}b, we report three cluster similarity curves (continent, language, language family) with varying scaling parameter $r$.
As expected, continent plays a major role at higher levels of clustering process (low $r$), language and language family explain the clustering process more at the lower levels (high $r$). 
This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.

@@

Using SemAxis, a technique unique to semantic embedding, we reconstruct geographic relationships and prestige hierarchies based defined axis between California and Massachusetts, and between lowly and highly ranked universities according to the Times Ranking of World Universities and the Leiden Ranking field-normalized citation impact (Fig.~\ref{fig:semaxis}). 
We find that, with a few exceptions, all universities in California are nearer the appropriate end of the axis than are Massachusetts universities, and \textit{vice versa}.
Universities in bordering states, such as Arizona and Connecticut, are closer to the ends of the axis (Fig. SI~\ref{fig:supp:semaxis_states}b and Fig. SI~\ref{fig:supp:semaxis_states}e). 
Universities in new York are nearer to the Massachusetts end of the axis (Fig. SI~\ref{fig:supp:semaxis_states}f), whereas universities in Florida are less aligned to either (Fig. SI~\ref{fig:supp:semaxis_states}i).

In terms of prestige, we find prestigious universities towards the top of the axis, such as Stanford, Colombia, MIT, Harvard, and NYU. 
Universities at the bottom of this axis tend to be regional universities with lower national profiles, such as California State University Long Beach, University of West Florida, and Barry University. 
There are strong differences by state in terms of prestige—overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (see Fig. SI~\ref{fig:supp:semaxis_states}).

Once these axes are constructed using university rankings, we can even relate other types of organizations that wouldn't typically be fit onto university rankings.
For example, among Government institutions, we see that the U.S. Department of Energy is more aligned with Californian universities, whereas the Mayo Clinic is more aligned with Massachusetts and organizations like the National Institute of Arthritis, Musculoskeletal, and Skin Disease and more aligned with elite universities than is the U.S. Department of Agriculture (Fig SI~\ref{fig:supp:semaxis_sectors}a).
Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig SI~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with lowly-ranked universities tend to be ecological or agricultural institutes such as the Joseph W. Jones Ecological Research Center and the Louisiana Agriculture Center. 
Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with lowly-ranked universities (Fig. SI~\ref{fig:supp:semaxis_sectors}c).

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\label{fig:semaxis}
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top). 
		Points correspond to organizations, and a sample of individual states are highlighted. 
		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
		The grey box corresponds to the top 20 and bottom 20 ranks. 
	  	The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
	}
\end{figure}

To what extent are semantic embeddings of mobility actually learning the latent hierarchy of academic mobility?
To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings. 
SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b). 
This correlation is robust with the number of organizations used to define the axes (Fig. SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$). 
For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$). 
This suggests that word embeddings, in addition to learning the latent geography of mobility, also capture more nuanced characteristics such as latent hierarchy.

@@

%
% Figure - Example of mobility sentences
%
\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.7\textwidth]{\figdir/mobility_example_combined.pdf}
	\caption{
		\textbf{Co-affiliation trajectories represented as sentences.}
		\textbf{a.} 
		An authors published five papers across five time periods, with only one affiliation listed in the byline of each paper. 
		A unique identifier is assigned to each organization, and these are concatenated into a mobility sentence. 
		\textbf{b.}
		In a more complex case, an author lists several affiliations on the byline of papers in $t_{2}$, $t_{3}$, and $t_{4}$. Here, organization ids are still ordered by year, however order within a single year is random.  	
	}
	\label{fig:methods:mobility_sentence}
\end{figure}

@@

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:pubs_over_time}
	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
	\caption{
		\textbf{Publications over time.}
		\textbf{a.}
		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
		Lines corresponds to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
		There is no evidence of major changes in publication patterns of mobile authors during this time period. 
		\textbf{b.}
		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased. 
		\textbf{c.} 
		Despite increasing absolute counts, the percentage of mobile scholars, and those with at least two city, regional, or country affiliations, as a proportion of all publications, has decreased over time. 
		\textbf{d.} 
		The proportion of authors publications across fields has largely remained steady.
		Biology and Health Science has comprised the majority of publications across nearly all years, but has steadily declined in proportion. 
		However, the proportion of Social Science and Humanities publications has been steadily increasing. 
	}
\end{figure}

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:pubs_over_time}
	\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
	\caption{
		\textbf{Extent and nature of mobility by country.}
		\textbf{a.}
		Proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study. 
		The countries with the most mobile researchers are the United States, China, France, Great Britain, and Germany. 
		\textbf{b.}
		The same information, arranged into a cumulative distribution.
		The five countires with the highest mobility account for approximately 70 percent of all mobility. 
		\textbf{c.} The proportion of researchers labeled as mobile by country.
		\textbf{d.} First two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries. 
		First component captures overall degree of mobile, whereas the second compares within-country against across-country mobility. 		
	}
\end{figure}

\newpage
%
% Figure - reverse CDF by scale
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:rcdf_by_scale}
	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
	\caption{
		\textbf{Reverse cumulative-distribution function of mobile authors by geographic scale.}
		\textbf{a.}
		Proportion of mobile authors by how many organizations are represented 	in their career trajectories. 
		For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
		Mobile authors are defined as those with at least two distinct organizational affiliations represented in our data. 
		\textbf{b.} 68 percent of mobile authors have at least two cities represented in their career trajectories.
		\textbf{c.} 45 percent of mobile authors have 2 or more regions represented in their career trajectories.
		\textbf{d.} Only 14 percent of mobile authors had 2 or more countries represented in their career trajectories. 
	}
\end{figure}

%
% Figure - Hyperparameter performance
%
\begin{figure}[p!]
	\centering
	\label{fig:supp:hyperparams}
	\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
	\caption{
		\textbf{Larger dimensions, smaller window size improves embedding performance.}
		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters. 
		Window size refers to the window, on either side of the target token, to use as context for training. 
		Smaller window sizes results in an embedding that explain more of the flux. 
		Embedding dimensions refer to the size of the organization vector.
		Larger vectors perform better, though little difference between 200 and 300. 
		All variants perform better on same-country pairs of organizations than on all organizations.
		All variants perform worse on different-country pairs on organizations.
		Larger embeddings outperform mid-size embeddings for the different-country case.
	}
\end{figure}

@@

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\label{fig:supp:semaxis_compare}
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
	\caption{
		\textbf{SemRank hierarchy is robust.}
		\textbf{a.} Spearman correlation (n = 143) between Times prestige rank and SemAxis rank, by the number of high and bottom-ranked (geographically matched) universities aggregated to form the poles. 
		More universities improves performance, but quickly saturates after around five universities. 
		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by number of universities used to define the poles (n). 
		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
		The grey box corresponds to the top 20 and bottom 20 ranks. 
	  	PCC details the estimate from Spearman correlation between the two rankings. 
	}
\end{figure}

%
% Figure - SemAxis By State
%
\begin{figure}[hp!]
	\centering
	\label{fig:supp:semaxis_states}
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis by U.S. state.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top). 
		Points correspond to universities shown for California (\textbf{a}), Arizona (\textbf{b}), Washington (\textbf{c}), Massachusetts (\textbf{d}), Connecticut (\textbf{e}), New York (\textbf{f}), Texas (\textbf{g}), Pennsylvania (\textbf{h}), and Florida (\textbf{i}).
		Grey points correspond to all other U.S. universities. 
	}
\end{figure}

%
% Figure - SemAxis By Sector
%
\begin{figure}[hp!]
	\centering
	\label{fig:supp:semaxis_sectors}
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top). 
		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching organizations, respectively.
		Grey points correspond to all U.S. universities.  
	}
\end{figure}

>>>>

A unique characteristic of semantic mobility embeddings is the ability to capture structure at multiple scales of granularity.
For example, just as the global embedding captures geographic structure between nations, so too does a projection or organizations in the United States reflect organizational structure based on states (Fig.~\ref{fig:projection}d). 
By re-projecting at the state-level for Massachusetts (Fig.~\ref{fig:projection}e), we observe structure between urban Centers (Boston vs. Worcester), but also based on organization type (hospitals tend to be adjacent) and different university systems. Even though UMass Boston is located in Boston, it clusters near other universities in the UMass System, reflecting a relative lack of mobility between the two systems, even within the same state. 
Similar dynamics can be observed in many states (New York, California, etc.), such that prestigious university systems are separate from more regional ones (See SI~?).

@@

What latent information do embeddings of scientific mobility capture, beyond geography?
We build on descriptive results to quantitatively assess the national factors captured in the learned vector-space.
We calculate the representative vector of each country with averaging organization vectors within the given country, calculate pairwise cosine similarity, and perform hierarchical clustering (see Fig. \ref{fig:clustering}a) of nations that have at least 25 organizations, excluding the United States which has high similarity with most other countries.

Six country clusters were identified, reflecting a mixture of the regional, linguistic, historical clusters, with clusters consisting of East-Asian (orange), Scandinavian (dark purple), British Commonwealth (light purple), Central and Eastern European countries (light blue), and then two cluster diverse clusters with a mix of European, Latin American, and Mediterranean countries.
When not defined by geography, clusters appear to be defined by linguistic and historical ties, as is the case for the commonwealth countries. 
There is a tendency that countries are grouped if they are in the same geographic region, if they are historically or culturally aligned, and if they share a similar language.

We investigate the extent to which geography and language dictate the formation of clusters using \textit{CluSim}~\autocite{gates2019element}, a method that compares different groupings and, for hierarchical clustering, can adjust the relative importance of membership at different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.  
If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, similarity is based on higher levels. 
Fig. \ref{fig:clustering}b demonstrates that continent plays a major role at higher levels of clustering process (low $r$), and language family and then language explain the clustering process more at the lower levels (high $r$). 
This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.

@@

In addition to encoding national characteristics, the embedding also encodes domestic geography and latent hierarchy. 
We employ SemAxis~\autocite{an2018semaxis}, a tool utilizing the unique vector arithmetic of semantic embeddings, to project U.S. universities onto two defined axes. 
The first axis is geographic, defined using the mean vector of universities in California on one end, and Massachusetts on the other.
The second axis relates instead to prestige.
Universities hiring and mobility networks are known to exhbit latent pretige hierarchies ~\autocite{deville2014career, clauset2015hierarchy} that should be encoded in the embedding space. 
The elite end of the axis is defined as the top 20 U.S. universities according to the Times Ranking of World Universities, whereas the non-elite axis is defined as bottom-ranked geographically matched (by U.S. census region) set of universities. 
A university projected onto the axis corresponds to their nearness to the mean vector defining each pole.
With a few exceptions, all universities in California are nearer the appropriate end of the axis than are Massachusetts universities, and \textit{vice versa} (Fig.~\ref{fig:semaxis}).
Universities in bordering states, such as Arizona and Connecticut, are closer to the ends of the axis (Fig.~\ref{fig:supp:semaxis_states}b and Fig.~\ref{fig:supp:semaxis_states}e). 
Universities in new York are nearer to the Massachusetts end of the axis (Fig.~\ref{fig:supp:semaxis_states}f), whereas universities in Florida are less aligned to either (Fig.~\ref{fig:supp:semaxis_states}i).

Prestigious universities, such as Stanford, Colombia, MIT, Harvard, and NYU, group towards the top of the axis.
Universities at the bottom of this axis tend to be regional universities with lower national profiles, such as California State University Long Beach, University of West Florida, and Barry University. 
There are strong differences by state in terms of prestige---overall, universities in Massachusetts are nearer the \textit{Elite} end of the axis than are universities in Arizona, Connecticut, Pennsylvania, and Florida (see Fig.~\ref{fig:supp:semaxis_states}).

Once these axes are constructed using university rankings, we can even relate other types of organizations that wouldn't typically be fit onto university rankings.
For example, among Government institutions, we see that the U.S. Department of Energy is more aligned with Californian universities, whereas the Mayo Clinic is more aligned with Massachusetts and organizations like the National Institute of Arthritis, Musculoskeletal, and Skin Disease and more aligned with elite universities than is the U.S. Department of Agriculture (Fig.~\ref{fig:supp:semaxis_sectors}a).
Among research institutes, the most aligned with elite universities are typically those prestigious university-adjacent institutes such as the Whitehead Institute, the Broad Institute, and the Dana Faber institute (Fig.~\ref{fig:supp:semaxis_sectors}b); those institutes aligned with lowly-ranked universities tend to be ecological or agricultural institutes such as the Joseph W. Jones Ecological Research Center and the Louisiana Agriculture Center. 
Among teaching organizations, the top-ranked tend to be notable private liberal arts colleges such as Wellesley College and Carleton College, whereas community colleges and military colleges tend to be more aligned with lowly-ranked universities (Fig.~\ref{fig:supp:semaxis_sectors}c).

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_fig.pdf}
	\caption{
		\textbf{Embedding captures latent geography and prestige hierarchy.}
		\textbf{a.} illustrates SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top). 
		Points correspond to organizations, and a sample of individual states are highlighted. 
		\textbf{b.} Comparison between the ranking of organizations by their rank in the Times ranking and the SemAxis rank derived from the similarity to the \textit{Elite} end of the axis prestige axis \textit{a}.
		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
		The grey box corresponds to the top 20 and bottom 20 ranks. 
	  	The estimate of the spearman rank correlation between the SemAxis and Times ranking is 0.81 (n = 145).
	}
	\label{fig:semaxis}
\end{figure}

In addition to learning geography, its clear that the skip-gram model is also encoding the latent prestige hierarchies of academic mobility. 
To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings. 
SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b). 
This correlation is robust with the number of organizations used to define the axes (Fig. SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$). 
For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$). 
This suggests that word embeddings, in addition to learning the latent geography of mobility, also capture more nuanced characteristics such as latent hierarchy.

@@

@@

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/pubs_over_time.pdf}
	\caption{
		\textbf{Publications over time.}
		\textbf{a.}
		The number of papers published by mobile authors has been steadily increasing from 2008 to 2017, with a small decrease in 2018,  likely an artifact of the Web of Science indexing process.
		Lines corresponds to publications by mobile authors (org, purple), by authors with affiliations in at least two cities (blue), at least two regions (green), and at least two countries (yellow).
		There is no evidence of major changes in publication patterns of mobile authors during this time period. 
		\textbf{b.}
		Lines correspond to the proportion of publications classified as Biology and Health (black), Physics and Engineering (purple), Life and Earth Science (magenta), Social Science and Humanities (orange), and Math and Computer Science (yellow).
		The rate of publication in Biology and Health has leveled since about 2013, whereas the rate of publication in other fields has steadily increased. 
		\textbf{c.} 
		Despite increasing absolute counts, the percentage of mobile scholars, and those with at least two city, regional, or country affiliations, as a proportion of all publications, has decreased over time. 
		\textbf{d.} 
		The proportion of authors publications across fields has largely remained steady.
		Biology and Health Science has comprised the majority of publications across nearly all years, but has steadily declined in proportion. 
		However, the proportion of Social Science and Humanities publications has been steadily increasing. 
	}
	\label{fig:supp:pubs_over_time}
\end{figure}

%
% Figure - publications over time
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/mobility_by_country.pdf}
	\caption{
		\textbf{Extent and nature of mobility by country.}
		\textbf{a.}
		Proportion of researchers in each country classified as mobile, meaning that they have at least two organization affiliations within the period of study. 
		The countries with the most mobile researchers are the United States, China, France, Great Britain, and Germany. 
		\textbf{b.}
		The same information, arranged into a cumulative distribution.
		The five countires with the highest mobility account for approximately 70 percent of all mobility. 
		\textbf{c.} The proportion of researchers labeled as mobile by country.
		\textbf{d.} First two principal components of four variables: proportion in each country mobile across organizations, proportion mobile across cities, proportion mobile across regions, and proportion mobile across countries. 
		First component captures overall degree of mobile, whereas the second compares within-country against across-country mobility. 		
	}
	\label{fig:supp:pubs_over_time}
\end{figure}

\newpage
%
% Figure - reverse CDF by scale
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
	\caption{
		\textbf{Reverse cumulative-distribution function of mobile authors by geographic scale.}
		\textbf{a.}
		Proportion of mobile authors by how many organizations are represented 	in their career trajectories. 
		For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
		Mobile authors are defined as those with at least two distinct organizational affiliations represented in our data. 
		\textbf{b.} 68 percent of mobile authors have at least two cities represented in their career trajectories.
		\textbf{c.} 45 percent of mobile authors have 2 or more regions represented in their career trajectories.
		\textbf{d.} Only 14 percent of mobile authors had 2 or more countries represented in their career trajectories. 
	}
	\label{fig:supp:rcdf_by_scale}
\end{figure}

%
% Figure - Hyperparameter performance
%
\begin{figure}[p!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Descriptive/hyperparameter_performance.pdf}
	\caption{
		\textbf{Larger dimensions, smaller window size improves embedding performance.}
		The correlation, or amount of flux explained by the embedding distance with varying skip-gram negative sampling hyperparameters. 
		Window size refers to the window, on either side of the target token, to use as context for training. 
		Smaller window sizes results in an embedding that explain more of the flux. 
		Embedding dimensions refer to the size of the organization vector.
		Larger vectors perform better, though little difference between 200 and 300. 
		All variants perform better on same-country pairs of organizations than on all organizations.
		All variants perform worse on different-country pairs on organizations.
		Larger embeddings outperform mid-size embeddings for the different-country case.
	}
	\label{fig:supp:hyperparams}
\end{figure}

@@

%
% Figure - SemAxis results
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_compare_fig.pdf}
	\caption{
		\textbf{SemRank hierarchy is robust.}
		\textbf{a.} Spearman correlation (n = 143) between Times prestige rank and SemAxis rank, by the number of high and bottom-ranked (geographically matched) universities aggregated to form the poles. 
		More universities improves performance, but quickly saturates after around five universities. 
		\textbf{b - f.} Comparison between the Times and SemAxis ranks of universities, by number of universities used to define the poles (n). 
		White points are those top and bottom 20 universities aggregated to define the ends of the axis. 
		The grey box corresponds to the top 20 and bottom 20 ranks. 
	  	PCC details the estimate from Spearman correlation between the two rankings. 
	}
	\label{fig:supp:semaxis_compare}
\end{figure}

%
% Figure - SemAxis By State
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_states_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis by U.S. state.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top). 
		Points correspond to universities shown for California (\textbf{a}), Arizona (\textbf{b}), Washington (\textbf{c}), Massachusetts (\textbf{d}), Connecticut (\textbf{e}), New York (\textbf{f}), Texas (\textbf{g}), Pennsylvania (\textbf{h}), and Florida (\textbf{i}).
		Grey points correspond to all other U.S. universities. 
	}
	\label{fig:supp:semaxis_states}
\end{figure}

%
% Figure - SemAxis By Sector
%
\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/SemAxis/semaxis_sectors_fig.pdf}
	\caption{
		\textbf{Geography and prestige SemAxis in U.S. by Sector.}
		SemAxis projection along two axes, comparing California to Massachusetts universities (left to right), and between the top 20 and geographically-matched bottom 20 universities ranked by the 2018 Times Higher Education ranking of U.S. Universities (bottom to top). 
		Points correspond to organizations labeled as Government (\textbf{a}), Institute (\textbf{b}), and Teaching (\textbf{c}), corresponding to government organizations, research institutes, and teaching organizations, respectively.
		Grey points correspond to all U.S. universities.  
	}
	\label{fig:supp:semaxis_sectors}
\end{figure}
